Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-28 introduction/Subsections/Introduction.tex
Updates from Overleaf

There has been a noticeable shift in this tendency in recent years, with a growing emphasis on retrieval tasks in the symbolic and musicological domain. Several powerful open-source analysis frameworks have emerged for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, as well as advancements in MIDI to human-readable sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, and automatic lead sheet generation \cite{WeilAutomaticSignals}, among others.

The driving force behind this shift might be the recognition of the complexity of implementing heuristics and abstract fields of study. Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions that mimic these aspects \cite{Mullensiefen2003MeasuringJudgments} is a topic that has been previously explored \cite{Hernandez-Olivan2023SymbolicMethods}.

Still, it remains a vast and open challenge.

>>>>

Music similarity is a critical factor in query-by-example retrieval systems. However, similarity calculation and definition can differ depending on user needs and retrieval scenarios. While acoustic properties like voice, genre, melody, tempo, instrumentation, and rhythm contribute to similarity, personal preferences, and cultural context also play a significant role. For instance, a user may avoid a particular artist's music despite its similarity to their favorite artists due to the album cover. Moreover, the user's context, such as driving or running, can also influence their preference and perception of similarity.

Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users who are unfamiliar with most tracks. Retrieval systems often overlook the cultural, personal, and musical aspects of music information needs, rendering them less useful for non-expert users. Many people search for music based on emotions or usage context rather than bibliographic information.

### 2023-04-28 introduction/Subsections/Motivation.tex
Updates from Overleaf

This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a prominent organization in the music technology sector. A deeper understanding of music and its fundamental structures fulfills intellectual curiosity and generates potential advancements and benefits for the company's technical products and services.

>>>>

This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.

The MTG specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.

The collaboration with Epidemic Sound and the MTG aims to deepen our understanding of music and its fundamental structures, which could potentially lead to advancements and benefits for the company's technical products and services as well as academic research.
